---
title: "HW1"
author: "jiaying Ning"
date: "9/15/2020"
output: github_document
---

This is my solution to HW1

*Note*

1.meaningful variable / object names
2.readable code (one command per line; adequate whitespace and indentation; etc)
3.clearly-written text to explain code and results
4.a lack of superfluous code (no unused variables are defined; no extra library calls; ect)

```{r install package}
library(tidyverse)
```

## problem 1

For problem 1, I start off by creating tables that contain a random sample of size 10 from a standard Normal distribution, a logical vector indicating whether elements of the sample are greater than 0,a character vector of length 10,a factor vector of length 10, with 3 different factor “levels”
```{r Problem 1}

#Creating tables that contain a random sample of size 10 from a standard Normal distribution, a logical vector indicating whether elements of the sample are greater than 0,a character vector of length 10,a factor vector of length 10, with 3 different factor “levels”
Problem1_df =  tibble(
  vec1 = rnorm(10),
  vec2 = vec1 > 0,
  vec3 = c("a","b","c","d","e","f","g","h","i","j"),
  vec4 = factor(c("low","low","low","Med","Med","Med","Med","High","High","High"))
  )

```
Then I take means for each vector

```{r problem 1 mean}
mean(pull(Problem1_df,vec1))
mean(pull(Problem1_df,vec2))
mean(pull(Problem1_df,vec3))
mean(pull(Problem1_df,vec4))
```
I can take mean of numerical and logical number, but not character or factor.

applies the as.numeric function to the logical, character, and factor variables 
```{r}
as.numeric(pull(Problem1_df,vec1))
as.numeric(pull(Problem1_df,vec2))
as.numeric(pull(Problem1_df,vec3))
as.numeric(pull(Problem1_df,vec4))
```



convert the logical vector to numeric, and multiply the random sample by the result
convert the logical vector to a factor, and multiply the random sample by the result
convert the logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result

```{r}
as.numeric(pull(Problem1_df,vec2))*pull(Problem1_df,vec1)
as.factor(pull(Problem1_df,vec2))*pull(Problem1_df,vec1)
as.numeric(as.factor(pull(Problem1_df,vec2)))*pull(Problem1_df,vec1)

```



## problem 2


load the penguins dataset
```{r import data}
data("penguins", package = "palmerpenguins")
x= na.omit(pull(penguins,flipper_length_mm))


```


There are `r ncol(penguins)` variables in the dataset "penguins" 

they are 

- `r variable.names(penguins)` 

with corresponding class of:

- `r t(t(sapply(penguins, class)))`. 


The data contains total of `r nrow(penguins)` observations. The mean flipper length is `r mean(x)`mm.

Below is a scatterplot of flipper_length_mm (y) vs bill_length_mm (x); color points using the species variable
I have saved the plot by using ggsave

```{r scatterplot}

ggplot(data=penguins,mapping=aes(bill_length_mm,flipper_length_mm)) + geom_point(data=penguins, aes(bill_length_mm,species),colour = "salmon")
ggsave("scatter_plot.pdf", height = 4, width = 6)

```

