---
title: "HW1"
author: "jiaying Ning"
date: "9/15/2020"
output: github_document
---

This is my solution to HW1

*Note*

1.meaningful variable / object names
2.readable code (one command per line; adequate whitespace and indentation; etc)
3.clearly-written text to explain code and results
4.a lack of superfluous code (no unused variables are defined; no extra library calls; ect)

```{r install package}
library(tidyverse)
```

## problem 1

```{r Problem 1}

#Creating tables that contain a random sample of size 10 from a standard Normal distribution, a logical vector indicating whether elements of the sample are greater than 0,a character vector of length 10,a factor vector of length 10, with 3 different factor “levels”
Problem1_df =  tibble(
  vec1 = rnorm(10),
  vec2 = vec1 > 0,
  vec3 = c("a","b","c","d","e","f","g","h","i","j"),
  vec4 = factor(c("low","low","low","Med","Med","Med","Med","High","High","High"))
  )

```
Taking means for each vector

```{r problem 1 mean}
mean(pull(Problem1_df,vec1))
mean(pull(Problem1_df,vec2))
mean(pull(Problem1_df,vec3))
mean(pull(Problem1_df,vec4))
```
I can take mean of numerical and logical number, but not character or factor.


```{r}
as.numeric(pull(Problem1_df,vec1))
as.numeric(pull(Problem1_df,vec2))
as.numeric(pull(Problem1_df,vec3))
as.numeric(pull(Problem1_df,vec4))

as.numeric(pull(Problem1_df,vec2))*pull(Problem1_df,vec1)

```

## problem 2
